---
title: "Case Study01: Study of US Craft Beer and Breweries"
author: "Adeel & Amita"
date: "October 13, 2018"
output: html_document
---
## CASE STUDY 01 - October 18
## Introduction and Overview

In this report, we explore datasets for various `beers` and the `breweries` that produce them in the US. The steps and procedures taken for this analysis are detailed below. 

### Description

The initial data provided were in two separate datasets, one each for beers and breweries, which were combined into a single dataset.
The Beers dataset contains a list of 2410 US craft beers and Breweries dataset contains 558 US breweries. The datasets descriptions are as follows

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r, include=FALSE}
library(ggplot2)  # Data visualization
library(readr)    # CSV file I/O, e.g. the read_csv function
library(dplyr)    # Heavy use of this library
library(tidyr)
library(ggthemes) # for themes in ggplot
library(knitr)
library(kableExtra) # library to make the document more presentable
library('dplyr')
library('ggplot2')
library('kableExtra')
library('grid')
# Load the CSV files into a variable


Breweries <- read.csv("Breweries.csv")
Beers     <- read.csv("Beers.csv")

# Rename the coolumn name

names(Breweries)[2] <- 'Brewery Name'
names(Beers)[1] <- 'Beer Name'

data <- Breweries %>% group_by(State) %>% summarize(Count = n())


```
### 1. How many breweries are present in each state?

We answer this question by retrieving the value of `State` from the `Breweries` data.

Generate the plot, group by state

Graph shows the Colorado, Califorina and Michigan has the highest number of Breweries

```{r}
 

ggplot(data, aes(reorder(State, -Count), Count, label = Count)) + 
  geom_bar(stat = "identity", width = .85, fill=rainbow(51)) +
  theme(axis.text.x = element_text(angle=90, vjust=0.6), plot.title = element_text(hjust = 0.5))+
  geom_text(size = 2.5, position = position_stack(vjust = 1.18)) + 
  labs(x = 'State', y = 'Count') 
  grid.text("(Figure 1)", 0.90, 0.90)


```

### 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

As part of our analysis, we ensured that duplicate data within each dataset shared the same variable name in both sets. We can now merge them into a single dataset, using `full_join`.

```{r, include=FALSE}

# 2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

MergedData <- merge(Beers, Breweries, by.y = 'Brew_ID', by.x = 'Brewery_id')

Data.Head <- head(MergedData[,c('Beer Name', 'ABV', 'IBU', 'Style', 'Brewery Name', 'City', 'State')])
Data.Tail <- tail(MergedData[,c('Beer Name', 'ABV', 'IBU', 'Style', 'Brewery Name', 'City', 'State')])


```

```{r}

# Showing top 6 records from the merged data set
kable(Data.Head, format = "markdown", padding = 2)


# Showing last 6 records from the merged data set
kable(Data.Tail, format = "markdown", padding = 2)


```

### 3. Report the number of NA’s in each column.

To do this, we use a function (which returns `true` if a given value is NA, `false` otherwise, using `is.na`) and `sapply` to determine the number of missing values for each column within `BrewPub`.

Per the results, we find that there are a total of 62 ABV values missing, and 1005 IBU values missing. No other data is missing.
```{r, include=FALSE}

# 3.	Report the number of NA's in each column.

Data.NA <- sapply(MergedData[!complete.cases(MergedData),],
       function(y) length(which(is.na(y))))

library(plotrix)
slices <- Data.NA[c(4:6) ]
mytable <- Data.NA[c(4,5,6)]
mytable[3] <- 5
lbls <- paste(names(mytable), "-", mytable, sep="")

```

```{r}
pie(mytable, labels = lbls, main="Count of NAs in columns (Values missing)",col=c('pink','SteelBlue','red'))

```

```{r}
# Show the count for NA's in each column

kable(Data.NA, format = "markdown", padding = 2)

```

### 4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

We build two new datasets, `Bitter` and `FireWater`, from our `BrewPub` dataset, omitting NA values. We then group the relevant values by state, and summarise by the median of the relevant value.

```{r, include=FALSE}

# 4.	Compute the median alcohol content and international bitterness unit for each state. 
#     Plot a bar chart to compare.

MergedData.Median <-  MergedData[complete.cases((MergedData)),] %>% # Find all the data  without NA's in it.
    group_by(State) %>%                         # Group by data frmae by state
    dplyr::summarise(ABV = median(ABV), IBU = median(IBU))  # Summary that data to find out median for ABV and IBU

```

```{r}
ggplot2::ggplot(MergedData.Median, aes(reorder(State, -IBU), IBU, fill=IBU)) + geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle=90, vjust=0.6), plot.title = element_text(hjust = 0.5)) +
    labs(x = 'State', y = 'IBU') 
grid.text("(Figure 2)", 0.80, 0.90)

ggplot2::ggplot(MergedData.Median, aes(reorder(State, -ABV), ABV, fill = ABV)) + geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle=90, vjust=0.6), plot.title = element_text(hjust = 0.5)) + 
    labs(x = 'State', y = 'ABV') 
grid.text("(Figure 3)", 0.80, 0.90)

```
### 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

We use `which.max` on our `BrewPub` dataset, seeking specifically the maximum value in the `ABV` and `IBU` columns.

From this, we identify Colorado as having the beer with the highest ABV, at `.128`; and we identify Oregon has having the beer with the highest IBU, at `138`.

```{r, include = FALSE}

# 5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

ABV.Max <- MergedData[which.max(MergedData$ABV),]
IBU.MostBitter <- MergedData[which.max(MergedData$IBU),]

Data.Compare <- data.frame('Maximum_Alcoholic_Beer' = ABV.Max$State, 'ABV Max' = ABV.Max$ABV, 'Most_Bitter_State' = IBU.MostBitter$State, 'IBU Most' = IBU.MostBitter$IBU)

names(Data.Compare) <- c('Maximum Alcoholic Beer', 'Max ABV', 'Most Bitter State', 'Most IBU')

```
### 6. Summary statistics for the ABV variable.

We do this by calling `summary` on the `ABV` column in our `BrewPub` dataset.

```{r}

kable(Data.Compare, format = "markdown", padding = 2)

```

```{r, include=TRUE}

# 6.	Summary statistics for the ABV variable. ????
Data.Summary <- summary(MergedData$ABV)
boxplot(MergedData$ABV, notch=TRUE, 
  col=(c("gold","darkgreen")),
  main="Summary Statiscits for ABV Variable", xlab="tbo")


```

```{r}

Data.Summary 


```
### 7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

We utilize `ggplot` to plot a scatter plot of the data, using `IBU` and `ABV` as our variables.

Examination of this scatter plot and the regression line suggests that there is a positive, linear relationship between `IBU` and `ABV`.
```{r}
# 7. Draw a scatter plot to compare relationship between beer 
# bitterness and alcohol content
ggplot(MergedData, aes(x=MergedData$IBU, y= MergedData$ABV)) +
  geom_point(shape=1) +
   geom_smooth(method=lm) + # add linear regression line
  theme_economist() + 
  scale_color_economist()+
  theme(axis.text.x=element_text(size=rel(1.0)))+
ggtitle("Correlation between IBU and ABV ") +
  labs(x="IBU",y="ABV")
```

## Review and Conclusion

In this analysis, we examined data gleaned from two datasets regarding beers and breweries throughout the US. We examined the structure of this data, cleaned them, and combined them. We then performed various analyses, such as calculating median values for IBU and ABV by state, and determining which states had the beers with the highest ABV and IBU values. We finished by looking for a potential relationship between IBU and ABV, and found that there is evidence to suggest that a positive correlation exists between the two.









